Model_additionalAlts

### 2015-11-29 models/Model_additionalAlts.Rmd
exploring different subjective alts for liked_loved

### Data for full model - no alternatives
```{r full_model_data, message=FALSE, warning=FALSE}
speaker = read.csv("~/Desktop/Projects/scalar_implicature/models/model_data/L0_e10.csv")
listener = read.csv("~/Desktop/Projects/scalar_implicature/models/model_data/L1_e11.csv")
data.full = left_join(speaker, listener) %>%
  left_join(priors) %>%
  rowwise %>%
  select(scale, degree, stars, speaker.p, listener.p, prior.p) %>%
  mutate(listener.p = ifelse(is.na(listener.p), 0, listener.p)) %>%
  group_by(scale)
```

@@

Focus on `good_excellent`:
```{r}
focus_alts = function(target, combos, normalize=F) {
  if (is.null(combos)) {
    combos = data.frame(c(0, 0, 1, 0, 0),
                        c(0, 0.05, 0.9, 0.05, 0),
                        c(0, 0.1, 0.8, 0.1, 0),
                        c(0, 0.2, 0.6, 0.2, 0),
                        c(0, 0.25, 0.5, 0.25, 0))  
  }
  colnames(combos) = LETTERS[1:length(colnames(combos))]
  cors = c()
  for (i in 1:ncol(combos)) {
    ge.subset = data.full.extras[data.full.extras$scale == target, ]
    ge.subset[ge.subset$degree == "mid", "speaker.p"] = combos[, i]
    target.scalars = c("hi1", "hi2")
    # Run model)
    m1 = ge.subset %>%
      do(run.full(., alpha = 8, addMid = T, normalize=normalize))
    if (target == "some_all") {
      target.scalars = c("hi1", "low1")
      m1 = m1[m1$degree %in% target.scalars, ]  
    } else {
      m1 = m1[m1$degree %in% target.scalars, ]  
    }
    cors[i] = cor(m1$pred, m1$listener.p)  
  }
  cors

  i = which(cors == max(cors))
  # combos[i]
  ge.subset = data.full.extras[data.full.extras$scale == target, ]
    ge.subset[ge.subset$degree == "mid", "speaker.p"] = combos[, i]
  m1 = ge.subset %>%
    do(run.full(., alpha = 8, addMid = T))

  qplot(stars, listener.p, col=degree, 
        data=m1,
        ylab="Posterior p(rating | word)") + 
    geom_line(aes(y = pred), lty = 4)
  return(combos[i])
}

focus_alts("good_excellent", combos=NULL)
focus_alts("liked_loved", combos=NULL)
combos = data.frame(c(0, 1, 0, 0, 0),
                    c(0.05, 0.9, 0.05, 0, 0),
                    c(0.1, 0.8, 0.1, 0, 0),
                    c(0.2, 0.6, 0.2, 0, 0),
                    c(0.25, 0.5, 0.25, 0, 0))
focus_alts("some_all", combos=combos)
```

>>>>

### Data for full model - no alternatives
```{r full_model_data, message=FALSE, warning=FALSE}
speaker = read.csv("~/Desktop/Projects/scalar_implicature/models/model_data/L0_e10.csv")
listener = read.csv("~/Desktop/Projects/scalar_implicature/models/model_data/L1_e11.csv")
data.full = left_join(speaker, listener) %>%
  left_join(priors) %>%
  rowwise %>%
  select(scale, degree, stars, speaker.p, listener.p, prior.p) %>%
  mutate(listener.p = ifelse(is.na(listener.p), 0, listener.p)) %>%
  group_by(scale)

data.full$entropy = scales.entropy[data.full$scale, ]$Entropy
```

@@

Focus on single scalar fn()
```{r}
focus_alts = function(target, combos, normalize=F) {
  if (is.null(combos)) {
    combos = data.frame(c(0, 0, 1, 0, 0),
                        c(0, 0.05, 0.9, 0.05, 0),
                        c(0, 0.1, 0.8, 0.1, 0),
                        c(0, 0.2, 0.6, 0.2, 0),
                        c(0, 0.25, 0.5, 0.25, 0))  
  }
  colnames(combos) = LETTERS[1:length(colnames(combos))]
  cors = c()
  for (i in 1:ncol(combos)) {
    ge.subset = data.full.extras[data.full.extras$scale == target, ]
    ge.subset[ge.subset$degree == "mid", "speaker.p"] = combos[, i]
    target.scalars = c("hi1", "hi2")
    # Run model)
    m1 = ge.subset %>%
      do(run.full(., alpha = 1,
                  addMid = T, normalize=normalize))
    if (target == "some_all") {
      target.scalars = c("hi1", "low1")
      m1 = m1[m1$degree %in% target.scalars, ]  
    } else {
      m1 = m1[m1$degree %in% target.scalars, ]  
    }
    cors[i] = cor(m1$pred, m1$listener.p)  
  }
  cors

  i = which(cors == max(cors))[1]
  # combos[i]
  ge.subset = data.full.extras[data.full.extras$scale == target, ]
    ge.subset[ge.subset$degree == "mid", "speaker.p"] = combos[, i]
  m1 = ge.subset %>%
    do(run.full(., alpha = 1, addMid = T))

  qplot(stars, listener.p, col=degree, 
        data=m1,
        ylab="Posterior p(rating | word)") + 
    geom_line(aes(y = pred), lty = 4)
  return(c(combos[i], cors[i]))
}

combos = data.frame(c(0, 0, 1, 0, 0),
                    c(0, 0.05, 1, .05, 0),
                    c(0, 0.1, 1, .1, 0),
                    c(0.05, 0.1, 1, .1, 0.05),
                    c(0.1, 0.1, 1, .1, 0.1))  
focus_alts("liked_loved", combos=combos)
colnames(combos) = LETTERS[1:length(colnames(combos))]
focus_alts("good_excellent", combos=NULL)

combos = data.frame(c(0, 1, 0, 0, 0),
                    c(0.05, 0.9, 0.05, 0, 0),
                    c(0.1, 0.8, 0.1, 0, 0),
                    c(0.2, 0.6, 0.2, 0, 0),
                    c(0.25, 0.5, 0.25, 0, 0))
focus_alts("some_all", combos=combos)
```
